Leadership across cultures and contexts: an exploratory analysis

### 2020-04-15 leadership_across_cultures_contexts.Rmd

We then explored "features" in our data. There are numerous approaches to detecting features in matrix data such as ours, many of which employ various dimensionality reduction and clustering techniques. We used several methods to explore lower dimensional representations of these data that might reveal informative structure, including logistic PCA, non-negative matrix factorization (NMF), and agglomerative hierarchical cluster analysis. Logistic PCA generalizes Pearson's original formulation of PCA to find a projection of the natural parameters of the saturated model that minimizes the Bernoulli deviance [@logisticPCA]. NMF [@lee1999] finds a low rank approximation of the original matrix, $X \approx WH$, where $X$ is an $n \times p$ matrix, and $W$ and $H$ are $n \times k$ and $k \times p$ matrices, respectively; all elements of $X$, $W$ and $H$ are $\geq 0$; and, typically, $k << min(n,p)$. NMF estimates $W$ and $H$ by minimizing a measure of distance (typically the Frobenius norm or the Kullback-Leibler divergence) between $X$ and $WH$ [@gaujoux2010]. Agglomerative hierarchical cluster starts with all elements in their own cluster, and then uses a distance metric to combine the two closest clusters into a single cluster; the next two closest clusters are then combined, and so forth, until all elements belong to a single cluster. We computed distance between our binary vectors using $1-cor(x, y)$ (so that the distance between highly correlated variables is close to $0$, the distance between uncorrelated variables is close to $1$, and the distance between negatively correlated variables is close to $2$), and agglomerated using the Ward algorithm. We assessed the robustness of the clusters using the *pvclust* package [@suzuki_pvclust2006], which computes an unbiased probability that a cluster appears in bootstrapped samples. We used 10,000 bootstrapped samples.

@@

>>>>

We then used several methods to explore lower dimensional representations of these data that might reveal informative "features." These included logistic PCA, non-negative matrix factorization (NMF), and hierarchical cluster analysis. Logistic PCA generalizes Pearson's original formulation of PCA to find a projection of the natural parameters of the saturated model that minimizes the Bernoulli deviance [@logisticPCA].

NMF [@lee1999] finds a low rank approximation of the original matrix, $X \approx WH$, where $X$ is an $n \times p$ matrix, and $W$ and $H$ are $n \times k$ and $k \times p$ matrices, respectively; all elements of $X$, $W$ and $H$ are $\geq 0$; and, typically, $k << min(n,p)$. NMF estimates $W$ and $H$ by minimizing a measure of distance between $X$ and $WH$ [we used the default "brunet" algorithm, which uses the Kullback-Leibler divergence; @gaujoux2010].

Agglomerative hierarchical cluster analysis starts with all elements in their own cluster, and then uses a distance metric to combine the two closest clusters into a single cluster; the next two closest clusters are then combined, and so forth, until all elements belong to a single cluster. We computed distance between our binary vectors using $1-cor(x, y)$, and agglomerated using the Ward algorithm. We assessed the robustness of the clusters using the *pvclust* package [@suzuki_pvclust2006], which computes an unbiased probability that a cluster appears in bootstrapped samples. We used 10,000 bootstrapped samples.

@@

```{r}
num_removed <- sum(rowSums(leader_text2[all_study_vars]) == 0)
```

To investigate features in our data, we first removed `r num_removed` text records with no evidence for any variable.
